Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-02-04 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

# Step 1: Data Preparation
df_ttff_disrup <- df_aoi %>%
  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
  dplyr::select(
    Participant,
    TOI,
    Time_to_first_fixation.Disruptive_Person
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
    Disruption_Category = case_when(
      TOI %in% verbal_disruptions ~ "Verbal disruptions",
      TOI %in% physical_disruptions ~ "Physical disruptions",
      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
  drop_na() %>%
  filter(
    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
  ) %>%
  mutate(
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2),
    log_Disrup_time_fixation_sec = round(log(Disrup_time_fixation_sec), 2) # Log-transformed variable
  )

@@

>>>>

# Step 1: Data Preparation
df_ttff_disrup <- df_aoi %>%
  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
  dplyr::select(
    Participant,
    TOI,
    Time_to_first_fixation.Disruptive_Person
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
    Disruption_Category = case_when(
      TOI %in% verbal_disruptions ~ "Verbal disruptions",
      TOI %in% physical_disruptions ~ "Physical disruptions",
      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
  drop_na()

# Count total observations before filtering
total_count <- nrow(df_ttff_disrup)

# Count dropouts due to filtering conditions
dropout_count <- df_ttff_disrup %>%
  filter(Time_to_first_fixation.Disruptive_Person <= 0 | 
         Time_to_first_fixation.Disruptive_Person > 30000) %>%
  nrow()

dropout_percentage <- round((dropout_count / total_count) * 100, 2)

# Print the number and percentage of dropouts
cat("Number of dropouts due to filtering conditions:", dropout_count, "(", dropout_percentage, "%)\n")

# Apply final filtering
df_ttff_disrup <- df_ttff_disrup %>%
  filter(
    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
  ) %>%
  mutate(
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2),
    log_Disrup_time_fixation_sec = round(log(Disrup_time_fixation_sec), 2) # Log-transformed variable
  )

@@

##################### t-Test and Cohen's d ########################

# Perform independent t-test
log_t_test_ttff <- t.test(log_Disrup_time_fixation_sec ~ Group, 
                          data = df_ttff_disrup_participant_summary, 
                          var.equal = TRUE)

# Compute Cohen's d
log_cohen_d_ttff <- cohen.d(log_Disrup_time_fixation_sec ~ Group, 
                            data = df_ttff_disrup_participant_summary)

# Create APA-style table
log_t_test_result_ttff <- data.frame(
  "Group Comparison" = "Novice vs. Expert",
  "t-value" = round(log_t_test_ttff$statistic, 2),
  "df" = log_t_test_ttff$parameter,
  "p-value" = format.pval(log_t_test_ttff$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(log_t_test_ttff$estimate[1] - log_t_test_ttff$estimate[2], 2),
  "Cohen's d" = round(log_cohen_d_ttff$estimate, 2),
  "95% CI (d)" = paste0("[", round(log_cohen_d_ttff$conf.int[1], 2), ", ", 
                         round(log_cohen_d_ttff$conf.int[2], 2), "]")
)

# Display APA table
knitr::kable(log_t_test_result_ttff, 
             caption = "t-Test and Effect Size for Log-Transformed Time to First Fixation (AOI Disruptive Student)") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
